Master's Project Journal

### 2019-03-31 tex_files/Journal.tex

As a result of these changes I was able to get a scope image where there was plus minus 10 nanoseconds on the edge visible in screen. Down from 40 nanoseconds that I had had on Tuesday AM and down from the 40\% ish of the period with the divider in place. I did remove the divider for this testing to make things easier and as of Thursday 14/03 it had not been replaced. The plan is that next week I will reimplement the divider and once I have better aligned the 4 PLLs I have, go up to a 3x3 network.
\section*{Alignment}
Found another lingering PF issue this week that was narrowing the locking range. Other than that I spent the week aligning oscillators in order to have a network. 2x2 was fine, 3x3 was a struggle. The LF issue that I suspect exists maybe the source of the narrow locking range I have seen. It remains to be seen however as this week was conference paper writing week and as such things have been slow in other areas (also 2 assignments). Made a new loop filter this weekend without fractions which may be easier to debug (Pierre's suggestion).

>>>>

As a result of these changes I was able to get a scope image where there was plus minus 10 nanoseconds on the edge visible in screen. Down from 40 nanoseconds that I had had on Tuesday AM and down from the 40\% ish of the period with the divider in place. I did remove the divider for this testing to make things easier and as of Thursday 14/03 it had not been replaced. The plan is that next week I will reimplement the divider and once I have better aligned the 4 PLLs I have, go up to a 3x3 network.
\section*{Alignment}
Found another lingering PF issue this week that was narrowing the locking range. Other than that I spent the week aligning oscillators in order to have a network. 2x2 was fine, 3x3 was a struggle. The LF issue that I suspect exists maybe the source of the narrow locking range I have seen. It remains to be seen however as this week was conference paper writing week and as such things have been slow in other areas (also 2 assignments). Made a new loop filter this weekend without fractions which may be easier to debug (Pierre's suggestion).
\section*{2x2 Locking Well, Paper submitted}
Turns out that the problem with my ring oscillators was that I was driving things in the wrong direction due to double negation. Did eventually solve this on Friday AFTER the paper was submitted. Performance is great now, 3x3 should work well (fingers crossed) on Monday. Unfortunately I wanted to submit to a conference on Monday but a combination of issues likely means that the project will not compile the references so when I collect the 30 missing datapoints and go home to do that it will likely be too late.
